---
title: "dsproject"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dsproject}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction 

The goal of `dsproject` is to provide a fast and friendly way to import a file as a dataframe, create a new project, and install and load a package. The function, responsible for importing a file, supports a variety of file formats, which makes it convenient to import a file. The function, responsible for creating a project, allows you to set up all of the project's subdirectories and the initial contents. Lastly, the function, responsible for installing and loading a package, allows you to first check whether the package is installed or not, and to install the package and then load it, if it wasn't not installed.

## Installation

```{r setup,eval=FALSE}
# Run the code below to install the devtools package if it is not already installed
if(!require(devtools)){
  install.packages("devtools")
}

# Install the dsproject package from Github
devtools::install_github("malneyadi4/dsproject")

# Load the dsproject package
library(dsproject)
```
